Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-10 manuscript.Rmd
Incorporated new model fits

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)

@@

# settings for sampler 
numSavedSteps <- 1000    # total number of MCMC steps
adaptSteps <- 1000  # Number of steps to "tune" the samplers
burnInSteps <- 2000 
thinSteps <- 10
nChains <- 16
ncores <- 8  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
options(mc.cores=ncores)

@@

plotlims <- c(15,40,0,0.03)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

@@

legend(21,0.03,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)

text(17,0.028,'(e)',adj=0.5,cex=2.5)

@@

plotlims <- c(15,40,0,0.6)  
ticklocsy <- seq(0,0.6,0.2)    # locations of tick marks on y axis
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

text(17,0.55,'(f)',adj=0.5,cex=2.5)

@@

plotlims <- c(15,40,0,0.6)  
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,0.6,0.2)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.55,'(b)',adj=0.5,cex=2.5)

@@

# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.75,'(c)',adj=0.5,cex=2.5)

>>>>

processdata <- 1  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)

@@

# settings for sampler 
numSavedSteps <- 100000    # total number of MCMC steps
adaptSteps <- 1000  # Number of steps to "tune" the samplers
burnInSteps <- 2000 
thinSteps <- 10
nChains <- 16
ncores <- 8  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
options(mc.cores=ncores)

@@

plotlims <- c(15,40,0,0.04)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklocsy <- seq(0,0.04,0.01)    # locations of tick marks on y axis
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

@@

legend(21,0.04,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)

text(17,0.037,'(e)',adj=0.5,cex=2.5)

@@

@@

text(17,0.95,'(f)',adj=0.5,cex=2.5)

@@

plotlims <- c(15,40,0,1)  
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.95,'(b)',adj=0.5,cex=2.5)

@@

# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.95,'(c)',adj=0.5,cex=2.5)
